At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-12-19 manuscript/supporting_info.tex
addressing cosmetic changes from New Phy

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, 
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

\linenumbers
\beginsupplement
\clearpage

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses. All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}. Further details for unpublished networks may be found there.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l l m{8cm} |}
    \hline
    Network & Network type & Country & Original source  \\
    \hline
    M\_PL\_001  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_002  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_003  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citet{Barrett1987} \\
    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citet{Clements1923}  \\
    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citet{Dupont2003}  \\
    M\_PL\_009  & Pollination & Sweden & \citet{Elberling1999} \\
    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
    M\_PL\_011  & Pollination & Mauritius & \citet{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Portugal (Azores) & \citet{Olesen2002a}  \\
    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citet{Ollerton2003}  \\
    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citet{Hocking1968} \\
    M\_PL\_015  & Pollination & Greece (Athens) & \citet{Petanidou1991} \\
    M\_PL\_016  & Pollination & Spain (Andalucia) & \citet{Herrera1988} \\
    M\_PL\_017  & Pollination & U.K. (England) & \citet{Memmott2002} \\
    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citet{Inouye1988}  \\
    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citet{Kevan1970} \\
    M\_PL\_021  & Pollination & Japan (Kyoto) & \citet{Kato1990}  \\
    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citet{Mosquin1967} \\
    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citet{Motten1982}  \\
    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{McMullen1993}  \\
    M\_PL\_027  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_028  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_029  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_030  & Pollination & Venezuela & \citet{Ramirez1992} \\
    M\_PL\_031  & Pollination & Venezuela & \citet{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

\section*{Supporting information 2: R implementation of tuple-form regression}

@@

\section*{Supporting information 3: Repeating our analyses with proportion of shared partners}

@@

\section*{Supporting information 4: A test of connectance}

@@

\section*{Supporting information 5: Distributions of $p$-values for permuted networks}

@@

\section*{Supporting information 6: Details of within-family regressions}

>>>>

\author{Alyssa R. Cirtwill, Giulio V. Dalla Riva, Nick J. Baker,\\
Mikael Ohlsson, Isabelle Norstr\"{o}m, Inger-Marie Wohlfarth,\\
Joshua A. Thia, Daniel B. Stouffer}
\date{Article accepted: December 13, 2019}

@@

% \linenumbers
\beginsupplement
\clearpage

\section*{Notes S1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses. All networks beginning 'M\_PL\_' were collected from~\citet{weboflife}. Further details for unpublished networks may be found there.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l l m{8cm} |}
    \hline
    Network & Network type & Country & Original source  \\
    \hline
    M\_PL\_001  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_002  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_003  & Pollination & Chile & \citet{Arroyo1982}  \\
    M\_PL\_004  & Pollination & Canada (New Brunswick) & \citet{Barrett1987} \\
    M\_PL\_005  & Pollination & U.S.A. (Colorado) & \citet{Clements1923}  \\
    M\_PL\_006  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_007  & Pollination & U.K. (Norfolk) & \citet{Dicks2002} \\
    M\_PL\_008  & Pollination & Spain (Canary Islands) & \citet{Dupont2003}  \\
    M\_PL\_009  & Pollination & Sweden & \citet{Elberling1999} \\
    M\_PL\_010  & Pollination & Denmark (Greenland) & Elberling, H. \& Olesen, J. M. Unpub. \\
    M\_PL\_011  & Pollination & Mauritius & \citet{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Portugal (Azores) & \citet{Olesen2002a}  \\
    M\_PL\_013  & Pollination & South Africa (KwaZulu-Natal) & \citet{Ollerton2003}  \\
    M\_PL\_014  & Pollination & Canada (N.W.T.) & \citet{Hocking1968} \\
    M\_PL\_015  & Pollination & Greece (Athens) & \citet{Petanidou1991} \\
    M\_PL\_016  & Pollination & Spain (Andalucia) & \citet{Herrera1988} \\
    M\_PL\_017  & Pollination & U.K. (England) & \citet{Memmott2002} \\
    M\_PL\_018  & Pollination & Denmark & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & U.S.A. (Colorado) & \citet{Inouye1988}  \\
    M\_PL\_020  & Pollination & Canada (N.W.T.) & \citet{Kevan1970} \\
    M\_PL\_021  & Pollination & Japan (Kyoto) & \citet{Kato1990}  \\
    M\_PL\_022  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_023  & Pollination & Argentina (Mendoza) & \citet{Medan2002} \\
    M\_PL\_024  & Pollination & Canada (N.W.T.) & \citet{Mosquin1967} \\
    M\_PL\_025  & Pollination & U.S.A. (North Carolina) & \citet{Motten1982}  \\
    M\_PL\_026  & Pollination & Ecuador (Gal\'{a}pagos Islands) & \citet{McMullen1993}  \\
    M\_PL\_027  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_028  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_029  & Pollination & New Zealand (South Island) & \citet{Primack1983} \\
    M\_PL\_030  & Pollination & Venezuela & \citet{Ramirez1992} \\
    M\_PL\_031  & Pollination & Venezuela & \citet{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

\section*{Notes S2: R implementation of tuple-form regression}

@@

\section*{Notes S3: Repeating our analyses with proportion of shared partners}

@@

\section*{Notes S4: A test of connectance}

@@

\section*{Notes S5: Distributions of $p$-values for permuted networks}

@@

\section*{Notes S6: Details of within-family regressions}
